Corporate Security Solutions for BYOD.\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-14 MUSES_vs_BYOD_solutions.tex
Unifying KNOX and blackberry balance and re-writing

\subsection{Samsung's KNOX and Blackberry Balance}
\label{subsec:samsungblackberry}

@@

The solution is available since December 2013.
The main feature of this security package is the use of different containers, or environments, for business and personal sides. Each one even includes its own graphic configuration (wallpapers, colours, and so on), in order to be more easily recognised and distinguished by the user.
There will be needed introducing a password to enter into the business side and, once \textit{logged in} this container, no more passwords will be required for the business applications. The applications approved by the company IT department must meet Samsung's security standards and allow single sign-on. A Knox API will also be provided for the company to be capable of accessing over almost 205 predefined IT policies (the SAFE API grows this number to 475). Also, Knox would allow different VPNs for individual apps.
Regarding the information protection methods, data files saved by applications of each environment are encrypted with AES 256-bit algorithm, in such manner that only the appropriate container can access these files. In the same way, the user won't be able to share data between the two environments, e.g. creating separate contact lists so the user cannot send a contact from one side to the other, or if the user copies data to the clipboard in the Knox container, it won't be there in the personal container.

There are three main components in the device architecture:

\begin{itemize}
	\item \textit{Customizable Secure Boot}: This ensures that only verified and authorized software can run on the device. It is a primary component that forms the first line of defence against malicious attacks on devices with Samsung KNOX. In addition, Samsung Knox's Secure Boot technology allows the switch of the secure boot root certificate in a secure manner after the devices are shipped.
	\item \textit{TrustZone-based Integrity Measurement Architecture (TIMA)}: By a continuous integrity monitoring of the Linux kernel, it is possible to detect that the integrity of the kernel or the boot loader is violated, and to take a policy-driven action in response. One of these policy actions disables the kernel and powers down the device.
	\item \textit{Security Enhancements for Android}: This feature is the one referred to the separation of information based on confidentiality and integrity requirements. It isolates applications and data into different domains so that threats of tampering and bypassing of application security mechanisms are reduced while the amount of damage that can be caused by malicious or flawed applications is minimized.
\end{itemize}

It is important to take into account that if an enterprise decides to deploy this solution to secure its BYOD environment, it must yet work with certain Mobile Device Management (MDM) services, either cloud or server based. Samsung offers a list\footnote{\url{https://www.samsungknox.com/en/knox-mdm-feature-list}} of the MDM which Knox supports, each one with the number of supported policies.

@@

\subsection{BlackBerry Balance}
\label{subsec:blackberrybalance}

This security package was announced as a feature of BlackBerry 10 \cite{Blackberry_tool}. Nevertheless, it is available with BlackBerry Enterprise Service 10, which is a device management, security and app management for BlackBerry, iOS and Android devices. It is necessary to activate BlackBerry Balance for having available some security features, all related or similar to the aforementioned. For instance, a message is displayed when the user tries to copy work data and then paste it into personal apps. Also, user attempting for actions that are not permitted in the company ISP, or may cause secure work information to be in contact with personal applications, these actions won't be permitted.

>>>>

\subsection{Samsung KNOX and Blackberry Balance}
\label{subsec:samsungblackberry}

@@

The main feature of this security package is the use of different containers, or environments, for business and personal sides. Each one even includes its own graphic configuration (wallpapers, colours, and so on), in order to be more easily recognised and distinguished by the user.
A password is required in order to enter into the business side and, once \textit{logged in} in this container, no more passwords are needed for the business applications. The applications approved by the company IT department must meet Samsung security standards and, though it has been said that KNOX is a device-focused solution, it offered an API. This API would allow the company to access to over almost 205 predefined IT policies. With regard to information protection methods, data files saved by applications of each environment are encrypted with AES 256-bit algorithm, in such manner that only the appropriate container can access these files. In the same way, the user is not allowed to share data between the two environments.

Features in Blackberry Balance are similar. This security package was announced as a feature of BlackBerry 10. Nevertheless, it is available with BlackBerry Enterprise Service 10, which is a device management, security and app management for BlackBerry, iOS and Android devices. It is necessary to activate BlackBerry Balance for having available some security features, all related or similar to the aforementioned. For instance, a message is displayed when the user tries to copy work data and then paste it into personal apps. Also, user attempting for actions that are not permitted in the company ISP, or may cause secure work information to be in contact with personal applications, these actions won't be permitted.

As a summary, Blackberry Balance has little opportunity if Blackberry sales continue to decrease, as well as Samsung KNOX, which is still out of the market. With this situation, MUSES could be a good choice, because is device-independent, and is available as an open source tool for both devices and servers.

@@
